### 2018-06-04 VV570/HW2/assignment.tex
add some fulfillment

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages

@@

\section{Connected Space}
\begin{enumerate}
	\item
		\begin{proof}
			\begin{enumerate}
				\item (i) $\Rightarrow$ (ii) \\
					Suppose (ii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$, and both $U_1$ and $U_2$ are open.\\
					Thus, $U_1$ and $U_2$ are closed as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (ii) is true when (i) is true.
				\item (ii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is open as $U$ is closed.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to (ii).\\
					Thus the assumption fails and (i) holds true when (ii) is true. 
				\item (i)$\Rightarrow$(iii)\\
					Suppose (iii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and both $U_1$ and $U_2$ are closed.\\
					Thus, $U_1$ and $U_2$ are open as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (iii) is true when (i) is true.
				\item (iii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is closed as $U$ is open.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty closed subsets, which is contradictory to (iii).\\
					Thus the assumption fails and (i) holds true when (iii) is true. 
			\end{enumerate}
		\end{proof}
	\item
		\begin{proof}
			If (iv) is false, then there exists a continuous, surjective application from $X$ into $[0, 1]\subset U$, which can be denoted as $f$.\\
			$[0, 1]$ can be written as $[0, a) \cup [a, 1] \triangleq V_1 \cup V_2$, where $0 < a < 1$, $V_1$ and $V_2$ are closed. Denote $U_1 = f^{-1}(V_1)$ and  $U_2 = f^{-1}(V_2)$. \\
			As $f$ is surjective, it follows that $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and $U_1 \cap U_2 = \emptyset$. \\
			As $f$ is continous, it follows that $U_1$ and $U_2$ are also closed, $U_1 \cap U_2 = X$.\\
			Thus, it is contradictory to (iii) as $X$ can be written as the union of two disjoint, non-empty closed subsets.\\
			So, if (iv) is not true then (iii) is also false.
		\end{proof}
	\item 
		\begin{proof}
			If (iii) is false, then $X = U_1 \cup U_2$, where $U_1$ and $U_2$ are two disjoint, non-empty closed subsets.\\
			...
		\end{proof}
\end{enumerate}

@@

	\item
	  \begin{proof}
		\begin{enumerate}
			\item
				It's clear that $\emptyset$ is connected as $X$ is itself.\\
				For $A$ containing only 1 element, it is connected as it can no be written as the union of two disjoint non-empty closed subsets.
			\item
				If $A$ is not an interval and the corner cases in a) are excluded, then it can be written as union of non-empty, disjoint closed subsets. Thus $A$ is not connected.
			\item

		\end{enumerate}
	  \end{proof}

\end{enumerate}

@@

>>>>

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm,amssymb} % Math packages
\usepackage{mathrsfs}

@@

\section{Connected Space}
\begin{enumerate}
	\item
		\begin{proof}
			\begin{enumerate}
				\item (i) $\Rightarrow$ (ii) \\
					Suppose (ii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$, and both $U_1$ and $U_2$ are open.\\
					Thus, $U_1$ and $U_2$ are closed as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (ii) is true when (i) is true.
				\item (ii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is open as $U$ is closed.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty open subsets, which is contradictory to (ii).\\
					Thus the assumption fails and (i) holds true when (ii) is true. 
				\item (i)$\Rightarrow$(iii)\\
					Suppose (iii) is not true, which means $X = U_1 \cup U_2$, $U_1 \cap U_2 = \emptyset$, $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and both $U_1$ and $U_2$ are closed.\\
					Thus, $U_1$ and $U_2$ are open as $U_1 = U_2^\complement$ and $U_2 = U_1^\complement$.\\
					So, $U_1$ and $U_2$ are both open and closed in $X$, which is contradictory to (i).\\
					Thus the assumption fails and (iii) is true when (i) is true.
				\item (iii) $\Rightarrow$ (i)\\
					Suppose (i) is not true, which means there exists $U$ s.t. $U \subset X$, $U \neq \emptyset$ and $U$ is both open and closed in $X$.\\
					Thus, $U^\complement$ is closed as $U$ is open.\\
					As $X = U \cup U^\complement$, then $X$ can be written as the union of two disjoint, non-empty closed subsets, which is contradictory to (iii).\\
					Thus the assumption fails and (i) holds true when (iii) is true. 
			\end{enumerate}
		\end{proof}
	\item
		\begin{proof}
			If (iv) is false, then there exists a continuous, surjective application from $X$ into $[0, 1]\subset U$, which can be denoted as $f$.\\
			$[0, 1]$ can be written as $[0, a) \cup [a, 1] \triangleq V_1 \cup V_2$, where $0 < a < 1$, $V_1$ and $V_2$ are closed. Denote $U_1 = f^{-1}(V_1)$ and  $U_2 = f^{-1}(V_2)$. \\
			As $f$ is surjective, it follows that $U_1 \neq \emptyset$, $U_2 \neq \emptyset$ and $U_1 \cap U_2 = \emptyset$. \\
			As $f$ is continous, it follows that $U_1$ and $U_2$ are also closed, $U_1 \cap U_2 = X$.\\
			Thus, it is contradictory to (iii) as $X$ can be written as the union of two disjoint, non-empty closed subsets.\\
			So, if (iv) is not true then (iii) is also false.
		\end{proof}
	\item 
		\begin{proof}
			If (iii) is false, then $X = U_1 \cup U_2$, where $U_1$ and $U_2$ are two disjoint, non-empty closed subsets.\\
			(haven't figured out yet...)
		\end{proof}
\end{enumerate}

@@

	\item
	  \begin{proof}
		\begin{enumerate}
			\item
				It's clear that $\emptyset$ is connected as $X$ is itself.\\
				For $A$ containing only 1 element, it is connected as it can no be written as the union of two disjoint non-empty closed subsets.
			\item
				If $A$ is not an interval and the corner cases in a) are excluded, then it can be written as union of non-empty, disjoint closed subsets. Thus $A$ is not connected.
			\item
				\begin{enumerate}
					\item 
						The continuous bijection mapping $f$ can be given as 
						\begin{equation}
							f(x) = \frac{x-I_{min}}{I_{max} - I_{min}} (J_{max} - J{min})
						\end{equation} 
						where $I_{min}, I_{max}, J_{max}, J{min}$ are the limits of corresponding interval.\\
						The inverse continuous bijection can be constructed in the same way, which can be given as
						\begin{equation}
							f^{-1}(y) = \frac{y-J_{min}}{J_{max} - J_{min}} (I_{max} - I_{min})
						\end{equation}
					\item 
						Consider open interval $X = (0, 1)$, it is clear that $X$ is connected. As there exists a continous bijection mapping which maps $X$ to $\mathbb{R}$, thus $f(A) = \mathbb{R}$ is connected as well.
					\item 
						If $U$ is both open and closed, then $U^\complement$ is also both open and closed. As there must exist a minimum for a closed and non-empty set, $R = U \cup U^\complement$ is then bounded, which is false. Thus, the only subsets that are both open and closed in $\mathbb{R}$ are $\mathbb{R}$ and $\emptyset$, which is equivalent to say $\mathbb{R}$ is connected. 
				\end{enumerate}
		\end{enumerate}
	  \end{proof}
	\item 
		\begin{proof}
			For any connected set $A$, as is indicated above, $f(A)$ is also connected, where $f$ is a continuous function.\\
			And the connected subsets of $\mathbb{R}$ are all intervals.\\
			Then $f(X)$ is an interval of $\mathbb{R}$, which contains both $f(a)$ and $f(b)$.\\
			Thus, $f(X)$ contains both $f(a)$ and $f(b)$.
		\end{proof}
\end{enumerate}

@@

	\item
		\begin{proof}
			\begin{enumerate}
				\item
					Given an open covering $\mathscr{U}$ of $A$, an open covering of $X$ by throwing in the open subset $U_0 = X /\ A$. Since $X$ is compact, there exists finitely many sets $U_1, U_2, U_3, ... , U_n \in \mathscr{U}$ \ s.t. $X = U_0 \cup U_1 \cup ... \cup U_n$. Then $A \subseteq  U_1 \cup ... \cup U_n$, proving that $A$ is compact.
				\item
					(haven't figured out yet...)
			\end{enumerate}
		\end{proof}
